gij bent 2

### 2024-12-09 paper/paper.qmd
Add numbers about the dataset size

As this study is a follow-up on the *gij bent* study by @sevenants_zijt_2024, we will re-use the dataset used in that study. The dataset contains [TODO infix] social media posts from Belgium on the Twitter platform (now X). These tweets either contain the traditional *gij zijt* or the innovative *gij bent* construction. The tweets are tagged for the Flemish dialect region to which each tweet author belongs. In addition, gender information was estimated for each tweet author using *gender-from-name-r* [@sevenants_gender_2024]. Authors for whom gender could not be established were removed, to retain parity with @sevenants_zijt_2024. The dataset also contains a formality distinction for each tweet ("more formal", "more informal"), based on whether a tweet interacts with other people. If it does, the idea is that the tweet is conversation-like and thus more informal. Each tweet also has a unique (anonymised) identifier, so tweets can be grouped by author. This will prove especially useful for this study on individual variation, since we need several tweets in order to gauge the language use of a specific speaker. For each author, we also know many accounts they follow, and how many accounts they are followed by. This is a metric that is useful for our questions about network influences. For our analysis of individual variation, we retained only those authors who have at least 10 tweets in our dataset. We did this in order to guarantee a stable estimation of each speaker's language use. After all filtering operations, we were left with TODO tweets by TODO unique authors.

>>>>

As this study is a follow-up on the *gij bent* study by @sevenants_zijt_2024, we will re-use the dataset used in that study. The dataset contains `r num_tweets %>% formatn` social media posts from Belgium on the Twitter platform (now X). These tweets either contain the traditional *gij zijt* or the innovative *gij bent* construction. The tweets are tagged for the Flemish dialect region to which each tweet author belongs. In addition, gender information was estimated for each tweet author using *gender-from-name-r* [@sevenants_gender_2024]. Authors for whom gender could not be established were removed, to retain parity with @sevenants_zijt_2024. The dataset also contains a formality distinction for each tweet ("more formal", "more informal"), based on whether a tweet interacts with other people. If it does, the idea is that the tweet is conversation-like and thus more informal. Each tweet also has a unique (anonymised) identifier, so tweets can be grouped by author. This will prove especially useful for this study on individual variation, since we need several tweets in order to gauge the language use of a specific speaker. For each author, we also know many accounts they follow, and how many accounts they are followed by. This is a metric that is useful for our questions about network influences. For our analysis of individual variation, we retained only those authors who have at least 10 tweets in our dataset. We did this in order to guarantee a stable estimation of each speaker's language use. After all filtering operations, we were left with `r num_tweets_filtered %>% formatn` tweets by `r num_users_filtered %>% formatn` unique authors.
